\documentclass[11pt,a4paper]{article}
\title{Behaviour Analysis of Elderly using topic models}
\author{Kristin Rieping}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}

\section{Introduction}

- Monitoring the health of elderly people, mentaly & pysical\\
- to check if they can live alone without any additional help\\
- longtime health monitoring\\
- also to detect accidents\\
- health monitoring is done by professional trained people that visit the elderly people at there home and make several physical and mentaly test with them. This is a timeconsuming precedure for both patient and professional and is only a sample and does not represent the average health situation of a patient.\\
\\
If you want to do this task, checking if people are fit and can still live on their own, you can use cameras. But these are privacy sensitive and it is still a hard task to do activity reckognition on video material.\\

Therefore sensors are placed at important places in the home of people. Looking at the output of this sensor data is also for human not very informative, so we need to find better feature descriptions that can give more information to professionals who need to judge the patients fitness. These features can also be used for Machine Learning algorithm that fit the fitness of patients to the data.
So why shouldn't we use just an ML algorithm on this plaine data? A ML alg must be able to find the best features automatically?
To give good results with an ML alg you need enough labeled data. But labeling data is a expensive task, in the sense that is time consuming. It is also sometimes the case that the labeling task influences the behaviour of the people that do this task. That is why it is advantageous to use an unsupervised approach for finding the best features.

Also it might not be the goal to do activity recognition, but find other features which are more informative about the fitness of people.\\

Might be interesting to check with professionals how they check if a person is fit or not.




\end{document}